Stable Hot Spot Analysis (Draft)

### 2017-06-15 paper-main.tex
Replaced zoom with aggregation

\begin{figure}[htp]
  \begin{subfigure}{\linewidth}
    \caption{Upward for zoom}
    \includegraphics[width=\linewidth]{images/gen-zoom-sohup-1}
    \label{fig:UpwardZoom}
  \end{subfigure}
  \hspace{1em}
  \begin{subfigure}{\linewidth}
    \caption{Downward for zoom}
    \includegraphics[width=\linewidth]{images/gen-zoom-sohdown-1}
    \label{fig:DownwardZoom}
  \end{subfigure}
  \caption{SoH zoom}
  \label{fig:Zoom}
\end{figure}

@@

\section{Conclusions and Future Work} \label{sec:Conclusion}
In this work, we compared the Getis-Ord statistic with Focal Getis-Ord statisitic. We validate the result from \ref{TODO last paper} with a real world 
dataset an with a larger dataset. The dataset was only one month projected in one raster. 
We examined further parameters and evaluated that $G^*$ and Focal $G^*$ performe better if the weight
is higher.
Our results indicate a high Focal range for the upward property and a maximum of 65x65 for the downward property.
Therefore F should be not less than 65x65. 
If we calculate the SoH for the zoom level, Getis-Ord leads to better results. In general the zoom level 
has the least influence if $G^*$ or Focal $G^*$ performe better.
We assume that if Focal $G^*$ has a different focal size for a different zoom level, 
it performes better, but this is beyond the scope of this work.

With this work we made a step further to the optimal parametrisation for $G^*$ and Focal $G^*$.
Our results indicate that the parametrisation for $G^*$ and Focal $G^*$ besides what is defined as parent and child has a huge impact on the
stability of hotspots. Wrong parametrisation can lead to good results, the mean reaches for \SOHUP in the weight dimension around 0.6.
It can also lead to bad result, \SOHUP in the zoom dimension reaches nearly zero. Therefore we shown that it is important to have a metric
for the stability of hotspots. Also we presented indication which parametrisation should be avoided and which parametrisations are promising.
$G^*$ can also be applied to spatio-temporal data.
Therefore Focal $G^*$ should be also applied to the spatio-temporal data. 
We now have a good indication which weight and focal size is usefull.
We didn't evaluate the results on other month because we assume that they are similar But it is interesting to find clusters for different times in the day.
One could asume that at lunchtime there will be hotspots at restaurants and they are not consistent with the hotspots over one month.
All our results are based on the SoH. Further work should validate or improve this metric also for the temporal dimension.

>>>>

\begin{figure}[htp]
  \begin{subfigure}{\linewidth}
    \caption{Upward for aggregation}
    \includegraphics[width=\linewidth]{images/gen-zoom-sohup-1}
    \label{fig:UpwardZoom}
  \end{subfigure}
  \hspace{1em}
  \begin{subfigure}{\linewidth}
    \caption{Downward for aggregation}
    \includegraphics[width=\linewidth]{images/gen-zoom-sohdown-1}
    \label{fig:DownwardZoom}
  \end{subfigure}
  \caption{SoH aggregation}
  \label{fig:Zoom}
\end{figure}

@@

\section{Conclusions and Future Work} \label{sec:Conclusion}
In this work, we compared the Getis-Ord statistic with Focal Getis-Ord statisitic. We validate the result from \ref{TODO last paper} with a real world 
dataset an with a larger dataset. The dataset was only one month projected in one raster. 
We examined further parameters and evaluated that $G^*$ and Focal $G^*$ performe better if the weight
is higher.
Our results indicate a high Focal range for the upward property and a maximum of 65x65 for the downward property.
Therefore F should be not less than 65x65. 
If we calculate the SoH for the aggregation level, Getis-Ord leads to better results. In general the aggregation level 
has the least influence if $G^*$ or Focal $G^*$ performe better.
We assume that if Focal $G^*$ has a different focal size for a different aggregation level, 
it performes better, but this is beyond the scope of this work.

With this work we made a step further to the optimal parametrisation for $G^*$ and Focal $G^*$.
Our results indicate that the parametrisation for $G^*$ and Focal $G^*$ besides what is defined as parent and child has a huge impact on the
stability of hotspots. Wrong parametrisation can lead to good results, the mean reaches for \SOHUP in the weight dimension around 0.6.
It can also lead to bad result, \SOHUP in the aggregation dimension reaches nearly zero. Therefore we shown that it is important to have a metric
for the stability of hotspots. Also we presented indication which parametrisation should be avoided and which parametrisations are promising.
$G^*$ can also be applied to spatio-temporal data.
Therefore Focal $G^*$ should be also applied to the spatio-temporal data. 
We now have a good indication which weight and focal size is usefull.
We didn't evaluate the results on other month because we assume that they are similar But it is interesting to find clusters for different times in the day.
One could asume that at lunchtime there will be hotspots at restaurants and they are not consistent with the hotspots over one month.
All our results are based on the SoH. Further work should validate or improve this metric also for the temporal dimension.
